Think deep for reef resilience

### 2025-06-23 paper/paper_draft.qmd
Add analysis based on cover as a percentage of reef area

Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996]. Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling). Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality as it is assumed the high background mortality of juveniles includes thermal stress.

>>>>

Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996]. Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling). Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality. There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
